---
title: "Reproducible Research: Peer Assessment 1"
output: html_document
keep_md: true
---
load library used in code
```{r echo = FALSE ,warning=FALSE}
library(dplyr)
#library(reshape2)

```

## Loading and preprocessing the data

read the CSV file, put in a data frame called activity, generte some information about our dataframe like dimension and data!!

```{r echo = TRUE,warning=FALSE}
activity <- read.csv(unz("activity.zip", "activity.csv"), header=T, sep=",")
dim(activity)
head(activity,n=5)

```

## What is mean total number of steps taken per day?
first change the class of variable date (factor at first) to Date, second melt steps by date and interval to get list of steps for each day, then calculate mean at each day
```{r, warning=FALSE, echo = TRUE}
activity$date<-as.Date(activity$date,tz = "UTC")
meandata <- melt(activity, id.vars=c("date","interval"))
means_steps_day <- dcast(meandata, date~variable, mean)
head(means_steps_day,n=5)
```

## What is the average daily activity pattern?

```{r}

```


## Imputing missing values

```{r}

```


## Are there differences in activity patterns between weekdays and weekends?
```{r}

```

