---
title: "Reproducible Research: Peer Assessment 1"
output: html_document
keep_md: true
---
load library used in code
```{r echo = FALSE}
library(dplyr)
library(reshape2)

```

## Loading and preprocessing the data

read the CSV file, put in a data frame called activity, generte some information about our dataframe like dimension and data!!

```{r echo = TRUE}
activity <- read.csv(unz("activity.zip", "activity.csv"), header=T, sep=",")
dim(activity)
head(activity,n=5)

```

## What is mean total number of steps taken per day?
first change the class of date to Date, second select only complete cases from activity data framesteps_day<-distinct(select(activity, date,steps))
```{r, echo = TRUE}
activity$date<-as.Date(activity$date)
#activity <- activity[complete.cases(activity),])
meandata <- melt(activity, id=c("date","interval"))
means_steps_day <- dcast(meandata, date~variable, mean)
head(means_steps_day,n=5)
```

## What is the average daily activity pattern?

```{r}

```


## Imputing missing values

```{r}

```


## Are there differences in activity patterns between weekdays and weekends?
```{r}

```

